Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-05 paper/paper.tex
units
save some space with Fig 1

  \matrix[nodes={draw, fill=none, scale=1, shape=rectangle, minimum height=1cm, minimum width=1.5cm},
          row sep=2cm, column sep=4cm] {
   \node (synth) {Synthesize};
   &
   \node (verif) {Verify}; \\
   \node[draw=none] {};
   &
   \node[ellipse] (done) {Done}; \\
  };

@@

We performed our experiments on a 4-core, 3.07GHz Xeon X5667 with 50GB of RAM.

>>>>

  \matrix[nodes={draw, fill=none, scale=1, shape=rectangle, minimum height=1cm, minimum width=1.5cm},
          row sep=2cm, column sep=3cm] {
   \node (synth) {Synthesize};
   &
   \node (verif) {Verify}; %\\
   %\node[draw=none] {};
   &
   \node[ellipse] (done) {Done}; \\
  };

@@

We performed our experiments on a 4-core, 3.07\,GHz Xeon X5667 with 50\,GB of RAM.
